\documentclass[11pt]{article}

\input{tex/packages.tex}
\input{tex/macros.tex}

\addbibresource{references.bib}

\title{2025-tower-paper}
\author{John Kaushagen}
\date{September 2025}

\begin{document}

\maketitle

\section{Introduction}
This paper studies the rate at which measures converge in a tower-like Markov chain \cite{Young1998}.
Specifically, we investigate polynomial decay of correlations, which arise often in dynamical systems.
Our main contribution is a sharp first-order bound on the error terms of the renewal measure when delay is present, expanding on the work of Rogozin in \cite{Rogozin1973}., as well as a result giving bounds on the total variation distance.
We also provide possible refinements to the bound when the delay terms and the renewal rates are of the same order.


Just the standard abstract here.
What has been done before, and what is this related to?
\begin{itemize}
    \item Rogozin Paper
    \item That other guy who came up with the complex analysis stuff?
    \item Young Tower
    \item Decay of Correlations
    \item Renewal Theory
\end{itemize}

\section{Preliminaries}
Just put some initial results here.
What did Rogozin do?
What did Young do?
The helper lemmas for the convergence results can go here, although I feel like theres room for improvement here.

\section{Markov Results on Tower}
Here I'll show the results on the tower like stationarity, what the stationary measure is, etc.
I also need to give a proof of the renewal equation with the delay.

\section{Convergence Results for Bases and Measures}
Here, I'll give the proofs of the order estimates for the terms un, Un, Vn, and Rn.
Split the cases for alpha and beta.
Give the special case when I have monotonic sequences.
\input{sections/convergence.tex}


\section{Correlation (if I have time)}
What if the returns aren't independent but depend on the section they left from?

\section{Conclusion}
Summary of what I did, and maybe some future areas to work on.

\printbibliography

\end{document}
